% Background
% Motivation
% Definition af MCC
% Motivation - hvorfor er emnet interessant? - hvad får man ud af at bruge det?
%   - hvordan ser emnet ud overordnet set?
% Meta om hvordan vores survey er organiseret

% http://arxiv.org/ftp/arxiv/papers/1206/1206.1118.pdf
New idea are always emerging in the field of technology.
One relatively recent idea is cloud computing, which is the idea that computing services can be handled remotely.
If you consider different types of computer services the use for cloud computing becomes obvious, in that if the computing power or the storage capability of a 'cloud' could be used then that opens up for a lot of applications.
The general idea as mentioned is to offload computer services from being handled locally to being handled remotely. 
This could for example be to use the computation power of the cloud, or the storage capability of the cloud as that might be more efficient or effective than having it be handled locally in that resources might be constrained.

Another fairly recent idea is mobile computing, but this has the problem that resources can be severely constrained. 
If the idea of of cloud computing is extended to mobile devices, you get another fairly recent idea: Mobile Cloud Computing or MCC.

One definition for the term MCC is given in \citet{}:

%http://www.ijsr.net/archive/v3i6/MDIwMTQ4NDc=.pdf
\textit{"Mobile Cloud Computing at its simplest, refers to an infrastructure where both the data storage and the data processing happen outside of the mobile device. Mobile cloud applications move the computing power and data storage away from mobile phones and into the cloud, bringing applications and mobile computing to not just smartphone users but a much broader range of mobile subscribers"}

MCC is very interesting because using it means you can avoid intrinsic issues on mobile devices and get a better experience for the user. 
These issues are that the resources on mobile devices can be very resource, e.g not a lot of storage space, not a lot of computation power, the internet might also be slow or there might be frequent disconnects.
MCC can address these problems by offloading mobile applications to external resource providers. \citet{}. % http://homepage.cs.latrobe.edu.au/sloke/papers/1-s2.0-S0167739X12001318-main.pdf
As \citet{} mentions, mobile cloud computing is still at an early stage of development and the purpose of this survey is to get an idea of the state of the art and what has been accomplished in the field since the idea was first introduced. % http://arxiv.org/ftp/arxiv/papers/1206/1206.1118.pdf 

This survey will go into the different types of clouds you encounter in mobile cloud computing.
It will also go into what kind of services are available and what they can be used for, for example Software as a Service.
Which frameworks and architectures have been built around this idea of MCC will also be covered. 
Furthermore, there are issues that should be discussed such as how data communication is handled and what kind of trust and security MCC has. 
There are also open research challenges in the area that need to be discussed. 