There are three common services that clouds provide.
\begin{description}[style=nextline]
\item[Infrastructure as a Service (IaaS)]
Where an entire infrastructure is provided to the customer.
This includes, hardware, software and storage that the customer rents \citep{article:mobilecloudreviewinderkilde}.
With this the customer is able to run an arbitrary range of software that can include operating systems \citep{misc:indersuverymcc}.
Examples of IaaS systems are Amazon Elastic Cloud Computing \citep{misc:amazonelastic} and DigitalOcean \citep{misc:digitalocean}.

\item[Platform as a Service (PaaS)]
This can be thought of as a service market for the customer.
You get a predefined completed platform provided, including operating system, database and webserver \cite{article:mobilecloudreviewinderkilde}.
In that way you lower the customizability of your service, and is limited to use the tools provided by the service.
You are still able to host own developed applications though, if such a feature is provided.

In that way the view is a bit different from IaaS, where you pick a platform and customize it with tools to fit your needs.
If you go the PaaS way, you have some tools you want to utilize and based on that finds a platform provider which fits your needs of tools.

A few examples of PaaS are \citet{misc:appFog} and \citet{misc:heroku}.

\item[Software as a Service (SaaS)]
With the SaaS approach, you limit the scope even more.
In such a scenario, the service provides some given software that you can use.
This ensures that you don't have to install the Software on your own system, but can instead utilise something already installed elsewhere \citep{article:mobilecloudreviewinderkilde,misc:indersuverymcc}.
In that sense you are provided a simple interface, and your contribution is input and the service gives you some output.

Examples of such software hosted on a SaaS are DBMS and Google Docs \citep{article:mobilecloudreviewinderkildesecurity}. 
\end{description}
In that way, the customer have different alternatives to which service types they want to use.
Common to all of them is that they delegate computation and storage concerns from the customers own device, to some rented service in the cloud.

Does the customer need a full scale customizable service, somewhere in between, or merely want to do text editing without having software installed on his device.